\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-18 doc/flexiblesusy-paper.tex
fixing small typos

  When two loop corrections have been enabled in the SLHA
  file by setting entry $4$ of the FlexibleSUSY block to $2$ the user may
  also select individual corrections. Entries $9$,$10$,$11$ and $12$,
  correspond to two loop corrections of order $\oatas$, $\oabas$,
  $\oatplusabsq$ and $\oatauq$ respectively and will be disabled when
  the corresponding entry is set to zero. In this way, for example, in
  the NMSSM the user may decide not to use the partial corrections at
  order $\oatplusabsq$ and $\oatauq$, all of which have
  only been computed in the MSSM.

>>>>

When two-loop corrections have been enabled in the SLHA file by
setting entry $4$ of the \code{FlexibleSUSY} block to $2$ the user may
also select individual corrections.  The \code{FlexibleSUSY} block
entries $9$, $10$, $11$ and $12$, correspond to two-loop corrections
of the order $\oatas$, $\oabas$, $\oatplusabsq$ and $\oatauq$
respectively and will be disabled when the corresponding entry is set
to zero.  In this way, for example, in the NMSSM the user may decide
not to use the partial corrections at order $\oatplusabsq$ and
$\oatauq$, all of which have only been computed in the MSSM.
